Bayesian determination of the effect of a deep euctectic solvent on the structure of lipid monolayers

### 2018-08-31 reports/apssamp.tex
slight rearrange

%
\begin{figure}[b]
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC). Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
\end{figure}
%
We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of measurements at different surface concentration.
The model was applied to the study of four phospholipids monolayers by X-ray reflectometry (XRR), namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface.
Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
However, their values were constained to be self-consistent for a single lipid over multiple measurements at different surface pressures.

>>>>

%
\begin{figure}[b]
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC). Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
\end{figure}
%
We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of measurements at different surface concentration.
The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by X-ray reflectometry (XRR).
Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
However, their values were constained to be self-consistent for a single lipid over multiple measurements at different surface pressures.
